---
title: "Hillsborough"
execute:
  echo: false
  message: false
  warning: false
---


```{r}
library(tidycensus)
library(tidyverse)
library(sf)
library(leaflet)
library(viridis)

x <- read_rds("fl_data.rds")

# Filter data for Hillsborough County
Hillsborough_data <- x %>%
  filter(grepl("Hillsborough County", NAME))  # Filter rows where NAME contains "Hillsborough County"

```



```{r}
# Define a color palette
pal <- colorNumeric(
  palette = "viridis",  # Use the "viridis" color scale
  domain = Hillsborough_data$pct_doctorate  # Map to the pct_doctorate column
)

# Create the leaflet map
leaflet_map <- leaflet(Hillsborough_data) %>%
  addTiles() %>%  # Add base map tiles
  addPolygons(
    color = ~pal(pct_doctorate),  # Color polygons based on pct_doctorate
    weight = 1,                   # Border thickness
    opacity = 1,                  # Border opacity
    fillOpacity = 0.7,            # Fill opacity
    popup = ~paste(               # Popup text when clicking on a tract
      "Tract: ", NAME, "<br>",
      "Population: ", B01003_001, "<br>",
      "% Doctorate: ", round(pct_doctorate, 2), "%"
    ),
    highlightOptions = highlightOptions(
      weight = 2,                 # Highlight border thickness
      color = "white",            # Highlight border color
      fillOpacity = 0.9,          # Highlight fill opacity
      bringToFront = TRUE         # Bring highlighted tract to front
    )
  ) %>%
  addLegend(
    position = "bottomright",     # Position of the legend
    pal = pal,                    # Color palette
    values = ~pct_doctorate,      # Values for the legend
    title = "% Doctorate"         # Legend title
  )

# Display the map
leaflet_map


```

This map overlays doctorate degree attainment data on the greater Tampa Bay region, with specific focus on Hillsborough County. The visualization uses a color gradient from purple (0-1% doctorate holders) to yellow (6% doctorate holders), providing insight into the educational landscape of the area.
Hillsborough County shows several notable patterns in its doctorate degree distribution:

The majority of the county displays deep purple coloring, indicating that most neighborhoods have relatively low percentages (0-1%) of residents with doctorate degrees. This pattern is consistent across much of the suburban and rural areas of the county.
However, there are several notable clusters where higher concentrations of doctorate degree holders reside:

In the north Tampa area, particularly around the University of South Florida region, there are pockets of green and blue coloring, suggesting areas with 3-4% doctorate degree holders. This higher concentration likely reflects the presence of university faculty, researchers, and professionals associated with the academic institution.

The south Tampa peninsula shows some variation, with a mix of purple and blue areas, indicating slightly higher concentrations of doctorate holders in certain neighborhoods, particularly in some of the more affluent areas.
The eastern portions of Hillsborough County, extending toward Plant City and the rural areas, consistently show lower percentages, predominantly in the 0-1% range. This reflects the more rural, agricultural nature of these areas.