---
execute: 
  echo: false
  message: fasle
  warning: false
---

```{r}
library(tidycensus)
library(tidyverse)
library(plotly)
library(sf)
library(viridis)
library(leaflet)

x <- read_rds("fl_data.rds")

```

```{r}

# Convert the sf object to a data frame
fl_education_df <- x %>%
  st_as_sf() %>%
  st_centroid() %>%  # Get the centroid of each polygon
  st_coordinates() %>%  # Extract the coordinates
  as.data.frame() %>%
  cbind(x)  # Combine with the original data

# Create a color palette for the percentage of Bachelor's degrees
pal <- colorNumeric(palette = viridis(100), domain = fl_education_df$pct_bachelors)

# Create the interactive Leaflet map
leaflet_map <- leaflet(fl_education_df) %>%
  addTiles() %>%  # Add default OpenStreetMap tiles (street view)
  addProviderTiles(providers$Esri.WorldImagery, group = "Satellite View") %>%  # Add satellite view
  addCircleMarkers(
    lng = ~X,  # Longitude
    lat = ~Y,  # Latitude
    radius = 5,  # Marker size
    color = ~pal(pct_bachelors),  # Color by percentage of Bachelor's degree
    fillOpacity = 0.8,  # Marker opacity
    popup = ~paste("Tract: ", NAME, "<br>Bachelor's Degree: ", round(pct_bachelors, 2), "%")  # Popup text
  ) %>%
  addLayersControl(
    baseGroups = c("Street View", "Satellite View"),  # Layer control for switching views
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  addLegend(
    pal = pal,  # Color palette
    values = ~pct_bachelors,  # Values for the legend
    title = "Bachelor's Degree (%)",  # Legend title
    position = "bottomright"
  ) %>%
  setView(lng = -81.5158, lat = 27.6648, zoom = 7)  # Set initial view to Florida

# Display the map
leaflet_map

```



 This map shows the percentage of people in Florida with bachelors degrees or higher in different parts of the state. coastal areas generally showing darker purple coloring, indicating lower rates of bachelor's degree attainment (0-20%). This pattern is particularly shown along both the eastern and western coastlines. Central inland areas display lighter coloring, suggesting higher educational attainment rates (30-50%). You can see that major urban areas visable on the map (like around Tampa, St. Petersburg, and Fort. Lauderdale) showing a combination of education levels in some neighborhoods while adjacent neighborhoods have rather low attainment levels.  
